Studying public transit API query logs\\ to get an indication of travel flows

### 2015-12-21 paper.tex
small changes

\maketitle
\begin{abstract}
% Context
%Public transit schedules are made available on the Web in various ways, such as in a GTFS file, a route planning API, or through Linked Connections.
The iRail project hosts a route planning API for the Belgian railway company.
This webservice provides an answer to a route planning question with parameters such as ``departuretime'', ``from'' and ``to''.
% Need
In the field of urban planning, researchers need an indication of how people move between cities. 
%Yet, getting this data from official sources has proven to be troublesome.
% Task
In this paper, we analyse the query logs of the iRail API, to see whether it can tell us something about travel flows between cities in Belgium.
% Object
We studied queries for the year 2013, which contains an average of $\sim3000$ interesting queries per day ($\sim0.4\%$ of the amount of passengers per weekday).
% Findings
We illustrate \todo{X} interesting patterns that correspond to reality and we show an outlier in the data.
% Conclusion
Visualizing the data shows the query logs are a better representation than random data, yet more research is needed to understand how representative for travel flows they may be.
% Perspectives
In earlier work, we have suggested the Linked Data Fragments axis to discuss new approaches to publishing queryable public transit data for maximized use.
We suggest a discussion for gathering query logs when using Linked Data Fragments approaches.

@@

In 2013, we have started to use a MySQL table to store each request in a table, including User-Agent string, the timestamp, whether or not the request succeeded, the departure station and the desired station of arrival.
From an export of this table, we have filtered out only the route plannning queries that succeeded.
The resulting dataset, used for the rest of this paper, can be downloaded at \todo{\url{http://datawijs.be/iraillogs.zip}}.

@@

Today, iRail publishes the most recent 1000 requests done on the API as open data, each second, at \url{http://api.irail.be/logs/}.
This amounts today to an average of 200k queries to the API per day, as the API gained popularity thanks to apps like \emph{BeTrains}\footnote{\todo{\url{http://...}}} and \emph{Railer}\footnote{\todo{\url{http://...}}}.

>>>>

\maketitle
\begin{abstract}
% Context
%Public transit schedules are made available on the Web in various ways, such as in a GTFS file, a route planning API, or through Linked Connections.
The iRail project hosts a route planning API for the Belgian railway company.
This webservice provides an answer to a route planning question with parameters such as ``departuretime'', ``from'' and ``to''.
% Need
In the field of urban planning, researchers need an indication of how people move between cities. 
%Yet, getting this data from official sources has proven to be troublesome.
% Task
In this paper, we analyse the query logs of the iRail API, to see whether it can tell us something about travel flows between cities in Belgium.
% Object
We studied queries for the year 2013, which contains an average of $\sim3000$ interesting queries per day ($\sim0.4\%$ of the amount of passengers per weekday).
% Findings
We illustrate \todo{X} interesting patterns that correspond to reality and we show an outlier in the data.
% Conclusion
Visualizing the data shows the query logs are a better representation than random data, yet more research is needed to understand how representative for travel flows they may be.
% Perspectives
In earlier work, we have suggested the Linked Data Fragments axis to discuss new approaches to publish queryable public transit data.
We suggest a discussion for gathering query logs when using Linked Data Fragments approaches.

@@

In 2013, we have started to use a MySQL table to store each request in a table, including User-Agent string, the timestamp, whether or not the request succeeded, the departure station and the desired station of arrival.
From an export of this table, we have filtered out only the route plannning queries that succeeded.
The resulting dataset, used for the rest of this paper, can be downloaded at \todo{\url{http://datawijs.be/apilog.tar.gz}}.

@@

Today, iRail publishes the most recent 1000 requests done on the API as open data, each second, at \url{http://api.irail.be/logs/}.
This amounts today to an average of 86k queries to the API per day, as the API gained popularity thanks to apps like \emph{BeTrains}\footnote{\url{https://play.google.com/store/apps/details?id=tof.cv.mpp}} and \emph{Railer}\footnote{\url{http://railer.be/}}.
This amounts to $\sim11.4\%$ of all passengers\footnote{According to numbers of the railway maintainer Infrabel, 758,370 people take the train each day.}.
